Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-03-18 paper/manuscript.Rmd
Update manuscript.Rmd and manuscript.md

@@

@@

In total, 12 of 29 collared female caribou swam between islands in the Fogo
archipelago. Only 3 of these 12 had more than XX swimming events during the
study period; ~30% of the marked population swam at least once, whereas for
~10% of individuals these swimming events were relatively common, on average
occurring once every XX  days during ice-free seasons. We did not
detect any swimming events for the remaining 17 individuals. It remains unclear
whether these individuals do not swim, or whether swimming is rare for most caribou. 
We are also unable to draw conclusions about the prevalence of
swimming in the ocean by male caribou: our initial visual observation was of an
adult male, but our GPS data only included females.

>>>>

# IDs > 10 swimming
n10 <- length(icefree[, .N, ANIMAL_ID][N > 10]$N)

@@

ind <- edges[ANIMAL_ID == "FO2016011" | ANIMAL_ID == "FO2017001" | ANIMAL_ID == "FO2017013"]
indMean <- round(ind[, mean(islandlen)], digits = 0)

@@

In total, 12 of 29 collared female caribou swam between islands in the Fogo
archipelago. Only `r n10` of these 12 had more than 10 swimming events during the
study period; ~30% of the marked population swam at least once, whereas for
~10% of individuals these swimming events were relatively common, on average
occurring approximately every `r indMean` days during ice-free seasons. We did not
detect any swimming events for the remaining 17 individuals. It remains unclear
whether these individuals do not swim, or whether swimming is rare for most caribou. 
We are also unable to draw conclusions about the prevalence of
swimming in the ocean by male caribou: our initial visual observation was of an
adult male, but our GPS data only included females.
